Visit Scotland Notebook

### 2023-06-14 visit_scotland_notebook.Rmd
Activity Data Work

demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
activities <- read_csv(here("data/clean_data/activities_clean.csv"))
usa_visit_spend_region <- read_csv(here("data/clean_data/usa_visit_spend_region_clean.csv"))

@@

demographics_all %>% 
  ggplot(aes(x = year, y = visits, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = visits_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "No. of Visits (Million) \n",
       title = "Number of Visits Over Time") +
  scale_y_continuous(limits = c(0, 200), breaks = c(0, 100, 200)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
```

@@

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(age, mean_exp_per_visit), y = mean_exp_per_visit, fill = age == "45-54 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019") +
  coord_flip()
```

@@

```{r}
employment_demographics %>%
  group_by(employment_status) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = employment_status, y = mean_exp_per_visit, fill = employment_status == "Employed/self-employed (full or part time)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Employment",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Employment")
```

```{r}
employment_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(employment_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(employment_status, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Employment Status",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))

@@

```{r}
activities %>%
  group_by(tourism_activity) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(tourism_activity, mean_exp_per_visit), y = mean_exp_per_visit,
               fill = tourism_activity == "Shopping for Non-Regular Purchases"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Activity",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2013-2019") +
  coord_flip()
```

@@

international_2017_2019_visits <- international_visits %>%
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2017, 2018, 2019)) %>% 
  summarise(total_visits = sum(visits)) %>% 
  select(total_visits)

tibble(a = c("Domestic", "International"),
       b = c(domestic_2017_2019_visits$visits, international_2017_2019_visits$total_visits)) %>% 
  ggplot() +
  geom_col(aes(x = a, y = b)) +
  labs(
    x = "",
    y = "Visits \n",
    title = "Domestic vs. International Visits",
    subtitle = "2017-2019")
```

>>>>

demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
activities <- read_csv(here("data/clean_data/activities_clean.csv"))
usa_visit_spend_region <- read_csv(here("data/clean_data/usa_visit_spend_region_clean.csv"))

@@

demographics_all %>% 
  ggplot(aes(x = year, y = visits, group = 1)) +
  geom_line(size = 1.5, colour = "grey") +
  geom_point(aes(colour = visits_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "No. of Day Visits (Million) \n",
       title = "Annual Number of Day Visits") +
  scale_y_continuous(limits = c(0, 200), breaks = c(0, 100, 200)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
  theme(plot.title = element_text(size = 20, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))
```

@@

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_visits = mean(visits)) %>% 
  arrange(age) %>% 
  ggplot() +
  geom_col(aes(x = age, y = mean_visits, fill = age == "16-24 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Visits per Year (Million) \n",
    title = "Mean Visits 2013-2019") +
  coord_flip()
```

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp = mean(expenditure)) %>% 
  arrange(age) %>% 
  ggplot() +
  geom_col(aes(x = age, y = mean_exp, fill = age == "25-34 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Visits per Year (Million) \n",
    title = "Mean Visits 2013-2019") +
  coord_flip()
```

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = age, y = mean_exp_per_visit, fill = age == "45-54 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Annual Expenditure \n",
    title = "Mean Annual Expenditure 2013-2019") +
  coord_flip()
```

@@

```{r}
employment_demographics %>%
  group_by(employment_status) %>% 
  summarise(mean_exp = mean(expenditure)) %>% 
  ggplot() +
  geom_col(aes(x = employment_status, y = mean_exp, fill = employment_status == "Employed/self-employed (full or part time)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Employment",
    y = "Mean Annual Spend \n",
    title = "Mean Annual Spend 2013-2019") +
  coord_flip()
```

```{r}
employment_demographics %>%
  group_by(employment_status) %>% 
  summarise(mean_visits = mean(visits)) %>% 
  ggplot() +
  geom_col(aes(x = employment_status, y = mean_visits, fill = employment_status == "Employed/self-employed (full or part time)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Employment",
    y = "Mean Annual Visits \n",
    title = "Mean Annual Visits 2013-2019") +
  coord_flip()
```

```{r}
employment_demographics %>%
  group_by(employment_status) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = employment_status, y = mean_exp_per_visit, fill = employment_status == "Employed/self-employed (full or part time)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Employment",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019") +
  coord_flip()
```

```{r}
employment_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(employment_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(employment_status, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Employment Status",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Diff, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))

@@

```{r}
activities %>%
  group_by(tourism_activity) %>%
  summarise(mean_exp = mean(expenditure)) %>% 
  ggplot() +
  geom_col(aes(x = tourism_activity, y = mean_exp,
               fill = tourism_activity == "Eating Out"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Activity",
    y = "Mean Annual Spend \n",
    title = "Mean Annual Spend, 2013-2019") +
  coord_flip()
```

```{r}
activities %>%
  group_by(tourism_activity) %>%
  summarise(mean_visits = mean(visits)) %>% 
  ggplot() +
  geom_col(aes(x = tourism_activity, y = mean_visits,
               fill = tourism_activity == "Visited friends or family for leisure"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Activity",
    y = "Mean Annual Visits \n",
    title = "Mean Annual Visits, 2013-2019") +
  coord_flip()
```

```{r}
activities %>%
  group_by(tourism_activity) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = tourism_activity, y = mean_exp_per_visit,
               fill = tourism_activity == "Shopping for Non-Regular Purchases"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Activity",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2013-2019") +
  coord_flip()
```

@@

international_2017_2019_visits <- international_visits %>%
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2017, 2018, 2019)) %>% 
  summarise(mean_visits = mean(visits)) %>% 
  select(mean_visits)

tibble(a = c("Domestic", "International"),
       b = c(domestic_2017_2019_visits$visits, international_2017_2019_visits$mean_visits)) %>% 
  ggplot() +
  geom_col(aes(x = a, y = b)) +
  labs(
    x = "",
    y = "Visits \n",
    title = "Domestic vs. International Visits",
    subtitle = "2017-2019")
```
